{\it E}nKCF: Ensemble of Kernelized Correlation Filters for High-Speed Object Tracking

### 2017-09-08 wacv_for_review.tex
Hyperrefs added, spellcheck done

We use both fHoG \cite{felzenszwalb2010object} and color-naming
\cite{van2009learning} for the large area, translation filter,
$R_{t}^{L}$. This is because the fHoG applied to relatively larger
area is tended to be noisy and less discriminative and adding color
information makes the feature vector for the translation filter,
$R_{t}^{L}$, more robust to noise and more discriminative. Figure
\ref{fig:Filters}(b) shows an example of this translation filter. But,
this is not the case for the small area, translation filter,
$R_{t}^{S}$, because this translation filter does not contain much of
the background area around the target. Figure \ref{fig:Filters}(a)
shows an example of this translation filter. Lastly, we use both fHoG
and color-naming features again for the scale filter,
$R_{s}$. Although we are using the same feature representations for
the scale filter learning relatively smaller area just around the
target, the reason of using two feature sets is slightly different in
that the area to learn is too small for the fHoG to represent the area
well. In addition, the scale filter, explained earlier in the
algorithm \ref{alg:MKCF}, estimates the scale of a target by
correlating it with three candidate ROIs. This search may increase the
run-time complexity of the scale filter from $\mathcal{O}(n\log n)$ to
$\mathcal{O}(3(n\log n))$. To ensure actual filtering operations
practical, we use a smaller template size (i.e., 64$\times n$) for the
scale filter, $R_{s}$. The smaller template size does not degrade the
tracking performance neither because of 1) zero padding around the
target and 2) use of color feature.
\begin{comment}
The ROI considered by $R_{s}$ is resized to a smaller template
resolution ($64\times n$) as shown in Figure~\ref{fig:Filters}(c).
This leads to less discriminative shape features. To reduce the noise
in $R_{s}$, we concatenate color features.  The $R_{s}$ estimates the
scale by correlating the filter with three candidate ROIs as detailed
in algorithm~\ref{alg:MKCF}.  This increases the complexity from
$\mathcal{O}(n\log n)$ to $\mathcal{O}(3(n\log n))$ for $R_{s}$.  To
reduce the number of operations, we assign a smaller template size to
$R_{s}$.  This does not degrade the tracking performance due to two
reasons: (1) zero padding around the target and (2) integration of
color features. This way, we keep the run-time complexity of the
$R_{S}$ similar to $R_{t}^{L}$ and $R_{t}^{S}$ that only run
correlation filter on a single ROI. By reducing the template size of
$R_{s}$, fluctuating run-time performances among $R_{s}$ and,
$R_{t}^{L}$ and $R_{t}^{S}$, are avoided which is desired in embedded
systems.

>>>>

We use both fHoG \cite{felzenszwalb2010object} and color-naming
\cite{van2009learning} for the large area, translation filter,
$R_{t}^{L}$. This is because the fHoG applied to relatively larger
area tends to be noisy and less discriminative and adding color
information makes the feature vector for the translation filter,
$R_{t}^{L}$, more robust to noise and more discriminative. Figure
\ref{fig:Filters}(b) shows an example of this translation filter. But,
this is not the case for the small area, translation filter,
$R_{t}^{S}$, because this translation filter does not contain much of
the background area around the target. Figure \ref{fig:Filters}(a)
shows an example of this translation filter. Lastly, we use both fHoG
and color-naming features again for the scale filter,
$R_{s}$. Although we are using the same feature representations for
the scale filter learning relatively smaller area just around the
target, the reason of using two feature sets is slightly different in
that the area to learn is too small for the fHoG to represent the area
well. In addition, the scale filter, explained earlier in the
algorithm \ref{alg:MKCF}, estimates the scale of a target by
correlating it with three candidate ROIs. This search may increase the
run-time complexity of the scale filter from $\mathcal{O}(n\log n)$ to
$\mathcal{O}(3(n\log n))$. To ensure actual filtering operations
practical, we use a smaller template size (i.e., 64$\times n$) for the
scale filter, $R_{s}$. The smaller template size does not degrade the
tracking performance neither because of 1) zero padding around the
target and 2) use of color feature.
\begin{comment}
The ROI considered by $R_{s}$ is resized to a smaller template
resolution ($64\times n$) as shown in Figure~\ref{fig:Filters}(c).
This leads to less discriminative shape features. To reduce the noise
in $R_{s}$, we concatenate color features.  The $R_{s}$ estimates the
scale by correlating the filter with three candidate ROIs as detailed
in algorithm~\ref{alg:MKCF}.  This increases the complexity from
$\mathcal{O}(n\log n)$ to $\mathcal{O}(3(n\log n))$ for $R_{s}$.  To
reduce the number of operations, we assign a smaller template size to
$R_{s}$.  This does not degrade the tracking performance due to two
reasons: (1) zero padding around the target and (2) integration of
color features. This way, we keep the run-time complexity of the
$R_{S}$ similar to $R_{t}^{L}$ and $R_{t}^{S}$ that only run
correlation filter on a single ROI. By reducing the template size of
$R_{s}$, fluctuating run-time performances among $R_{s}$ and,
$R_{t}^{L}$ and $R_{t}^{S}$, are avoided which is desired in embedded
systems.
